Multifunctional Lipid Probes Background

### 2025-01-28 TrifunctionalLipidProbesOverview.qmd
tiny formatting change

References to include: 
* [@schultzFlashClickMultifunctionalized2022a]
* [@schultzChemicalToolsLipid2023]
* [@farleyTrifunctionalSphinganineNew2024a]
* [@hoglingerTrifunctionalLipidProbes2017]

@@

References to include: 
* [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014

@@

Pros:
* Widely used, though not strictly a direct measurement of relative abundance. Highly accessible, as label-free quantification is much less costly and sample preparation is much more simple.

Cons:
* Co-elution of high- and low-abundance peptides can cause significant issues in the number of peptides can be isolated in MS1. 
* Samples are necessarily run at different times. Instrument calibration can drift, contaminants in the liquid chromatography can build, and errors can accrue in the preparation of each sample. Unless great care is taken, substantial differences between MS runs can result in the reporting of artificial differences between the samples.

@@

Pros:
* Because many (16+ in the case of Tandem Mass Tags^TM^) samples can be pooled in each experimental group, the total number of MS runs can be reduced. Alternatively, the pooled experimental group can be fractionated (typically orthogonally to the reverse phase chromatography used in the LC injection method; e.g. cation exchange) so that high-abundance and low-abundance proteins can be spaced out. 
  * For example, instead of performing 16 individual low-depth MS runs using label-free methods, one may run 6 fractionated MS runs of the pooled experimental group, resulting in significantly greater depth of MS1 peptide coverage.

Cons:
* Cost
* Increased number of sample preparation steps, higher probability to introduce variation in sample handling.
* Requirement for normalizing total protein input: when comparing +UV to -UV in diazirine enrichment, one necessarily must artificially combine disproportionate sample quantities. [We might not want to mention this here, it's a niche issue...]
* Need for greater precision in MS scanning -- more expensive instruments and outsourcing of sample analysis.

>>>>

References to include:

* [@schultzFlashClickMultifunctionalized2022a]
* [@schultzChemicalToolsLipid2023]
* [@farleyTrifunctionalSphinganineNew2024a]
* [@hoglingerTrifunctionalLipidProbes2017]

@@

References to include:

* [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014

@@

Pros:

* Widely used, though not strictly a direct measurement of relative abundance. Highly accessible, as label-free quantification is much less costly and sample preparation is much more simple.

Cons:

* Co-elution of high- and low-abundance peptides can cause significant issues in the number of peptides can be isolated in MS1. 
* Samples are necessarily run at different times. Instrument calibration can drift, contaminants in the liquid chromatography can build, and errors can accrue in the preparation of each sample. Unless great care is taken, substantial differences between MS runs can result in the reporting of artificial differences between the samples.

@@

Pros:

* Because many (16+ in the case of Tandem Mass Tags^TM^) samples can be pooled in each experimental group, the total number of MS runs can be reduced. Alternatively, the pooled experimental group can be fractionated (typically orthogonally to the reverse phase chromatography used in the LC injection method; e.g. cation exchange) so that high-abundance and low-abundance proteins can be spaced out. 
  * For example, instead of performing 16 individual low-depth MS runs using label-free methods, one may run 6 fractionated MS runs of the pooled experimental group, resulting in significantly greater depth of MS1 peptide coverage.

Cons:

* Cost
* Increased number of sample preparation steps, higher probability to introduce variation in sample handling.
* Requirement for normalizing total protein input: when comparing +UV to -UV in diazirine enrichment, one necessarily must artificially combine disproportionate sample quantities. [We might not want to mention this here, it's a niche issue...]
* Need for greater precision in MS scanning -- more expensive instruments and outsourcing of sample analysis.
